---
title: "BrookeSJ_Barbenheimer_Lecture_Week03"
author: "Siân Brooke"
date: "2024-01-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 

# Remember to install packages if you haven't used them before.
# install.packages("tidytext")

library(dplyr)
library(tidytext)
library(readtext)
library(tm)
library(ggplot2)
library(reshape)
library(sentimentr)

```

## Data Reading In
Load in the Reddit / Barbenheimer Data


The pipe operator, written as %>% , is a longstanding feature of the magrittr package for R. 
It takes the output of one function and passes it into another function as an argument. 
This allows us to link a sequence of analysis steps.

```{r}
barbenheimer_posts <- read.csv("~/PycharmProjects/Edi_Lecture/Data/Barbenheimer_Reddit_Posts.csv")
barbie_posts <- read.csv("~/PycharmProjects/Edi_Lecture/Data/Barbie_Reddit_Posts.csv")
oppi_posts <- read.csv("~/PycharmProjects/Edi_Lecture/Data/Oppenheimer_Reddit_Posts.csv")

data_list <- list(barbenheimer_posts, barbie_posts, oppi_posts)
barbenheimer_data <- merge_recurse(data_list)

 barbenheimer_data <- barbenheimer_data[!(is.na(barbenheimer_data$Post.Text) | barbenheimer_data$Post.Text==""), ]
 
str(barbenheimer_data)

```

## Text Pre-Processing 

You can convert a text column to lowercase using the tolower() function. This function is vectorized, meaning it can be applied to each element of a vector (or a column in a data frame) without the need for explicit looping. 

In this code snippet:

- tolower(df$text_column) converts each entry in text_column to lowercase.
- df$text_column <- ... replaces the original text_column in your data frame with these lowercase versions.

```{r}
# Convert the text column to lowercase
barbenheimer_data$Post.Title <- tolower(barbenheimer_data$Post.Title)
barbenheimer_data$Post.Text <- tolower(barbenheimer_data$Post.Text)
```

In the code below, we create a corpus from the text column, tokenize the corpus using word_tokenizer, and then convert the tokenized corpus back to a data frame for easy viewing. This will tokenize the text in the specified column into individual words.

The resulting tokenized_data data frame will have two columns: "text_column" (containing the original text) and "word" (containing individual word tokens).

Note that you'll need to have the dplyr package loaded as well since unnest_tokens() is part of the tidyverse.


```{r}

tidy_barbenheimer <- barbenheimer_data %>% 
  # Tokenize the text column using unnest_tokens()
  unnest_tokens(word, Post.Text, strip_punct = TRUE)



tidy_barbenheimer_words <- tidy_barbenheimer %>% 
  # Remove the stop words
  anti_join(stop_words)
  
tidy_barbenheimer_words <- tidy_barbenheimer_words[!tidy_barbenheimer_words$word %in% as.character(c(0:100)),]

```
count the words

```{r}
word_count <- head(tidy_barbenheimer_words %>% count(word, sort=TRUE), 10)

library(ggplot2)
# Basic barplot
p <- ggplot(data=head(tidy_barbenheimer_words %>% count(word, sort=TRUE), 10), 
            aes(x=word, y=n)) +
  geom_bar(stat="identity") + 
  labs(x = "Word", y = "Frequency in Dataset") +
  theme_minimal()
p

```

Plot sentiment of entire post over time

```{r}
# converting to datetime object 
barbenheimer_data$Post.Sentiment <- sapply(barbenheimer_data$Post.Text, function(x) 
                             mean(sentiment(x)$sentiment))

barbenheimer_data$Post.Date <- as.Date(barbenheimer_data$Post.Date)
```
Plot
```{r}

p <- ggplot(aes(x = Post.Date, y = Post.Sentiment), 
            data = barbenheimer_data) + 
  geom_point() + 
  labs(x = "Date of Reddit Post", y = "Sentiment of Post")

p + stat_smooth(method = "loess", formula = y ~ x, size = 1)



```



